Design and Implementation of Probabilistic Programming Language Anglican

### 2017-03-16 paper/paper.tex
fixed Franks email
forgot to commit changes

\author{Frank Wood}
\affiliation{\institution{University of Oxford}}
\email{fwood@cs.ox.ac.uk}

@@

The purpose of probabilistic forms \texttt{sample} and
\texttt{observe} is to interrupt deterministic computation and
transfer control to the inference algorithm.  Practically, this
is achieved by returning a record that represents the state of program execution at the checkpoint, rather than invoking a continuation. The Clojure record used to interrupt execution at 
\texttt{sample} and \texttt{observe} forms are \texttt{anglican.{\linebreak[0]}trap.{\linebreak[0]}sample} and \texttt{anglican.{\linebreak[0]}trap.{\linebreak[0]}observe} respectively. These records contain a unique identifier (which we will discuss in detail in section \ref{sec:addressing}), the arguments to the special form, the continuation, and the state.
\begin{lstlisting}[style=default]
=> (cps-of-expression '(sample dist) cont)
(->sample 'S1 dist cont $state)
=> (cps-of-expression '(observe dist v) cont)
(->observe 'O1 dist v cont $state)
\end{lstlisting}
Here \texttt{->sample} and \texttt{->observe} in the
CPS-transformed expressions are constructors for Clojure
records, and they take values of their fields as arguments.
Calling the continuation resumes the computation.

>>>>

\author{Frank Wood}
\affiliation{\institution{University of Oxford}}
\email{fwood@robots.ox.ac.uk}

@@

The purpose of probabilistic forms \texttt{sample} and
\texttt{observe} is to interrupt deterministic computation and
transfer control to the inference algorithm.  Practically, this
is achieved by returning a record that represents the state of program execution at the checkpoint, rather than invoking a continuation. The Clojure record used to interrupt execution at 
\texttt{sample} and \texttt{observe} forms are \texttt{anglican.{\linebreak[0]}trap.{\linebreak[0]}sample} and \texttt{anglican.{\linebreak[0]}trap.{\linebreak[0]}observe} respectively. These records contain a unique identifier (which we will discuss in detail in section \ref{sec:addressing}), the arguments to the special form, the continuation, and the state.
\begin{lstlisting}[style=default]
=> (cps-of-expression '(sample dist) 'cont)
(->sample S1 dist cont $state)
=> (cps-of-expression '(observe dist v) 'cont)
(->observe O1 dist v cont $state)
\end{lstlisting}
Here \texttt{->sample} and \texttt{->observe} in the
CPS-transformed expressions are constructors for Clojure
records, and they take values of their fields as arguments.
Calling the continuation resumes the computation.
